---
title: "Untitled"
author: "Farnadis_Kanja"
date: "2/11/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Let's begin by loading the dependancies and their libraries
```{r}
install.packages("data.table") # install package data.table to work with data tables
library("data.table")
```

```{r}
install.packages("tidyverse") # install packages to work with data frame - extends into visualization
library(tidyverse)
```

```{r}
library(caret)
```

Let's load dataset and preview it
```{r}
supermarket <- fread('http://bit.ly/CarreFourDataset')
head(supermarket)
```
Let's look at various properties of the dataset
```{r}
str(supermarket)
```

```{r}
dim(supermarket)
#1000 rows and 16 columns
```

```{r}
class(supermarket)
```
Data Cleaning
Lets check for null values
```{r}
sum(is.na(supermarket))
#no null values
```
Let's look at duplicated values
```{r}
duplicated_rows <- supermarket[duplicated(supermarket),]
duplicated_rows
#no duplicated rows
```
Let's drop some columns- col id, date, time
```{r}
supermarket2= within(supermarket, rm("Invoice ID", "Date", "Time", "gross margin percentage"))
```
preview 
```{r}
head(supermarket2)
```


Select categorical variables

```{r}
#select categorical variables
supa <- supermarket2[,c(1,2,3,4,8)]
#non categorical
market <- supermarket2[,c(5,6,7,9,10,11,12)]

```
encode supa
```{r}
dmy <- dummyVars(" ~ .", data = supa, fullRank = T)
df <- data.frame(predict(dmy, newdata = supa))
```
join newly encoded plus market
```{r}
carrefour <- cbind(market,df)


```
Dimensionality Reduction- pca
```{r}
data_pca <- prcomp(carrefour, scale = F,
                center = TRUE, retx = T)
names(data_pca)
```

```{r}
summary(data_pca)
#there are 19 Principle components with the first explaining 99% of the total variance
```
Let's plot the pca
```{r}
library(devtools)
install_github("vqv/ggbiplot", force = TRUE)
```
Load the ggbiplot library
```{r}
install.packages("grid")
```

```{r}
library(ggbiplot)
```

```{r}
ggbiplot(data_pca)
```
The first four variables seem to the most important although in reality, the first one seems to carry all the wieght. 
Part 2- Feature Selection
Let's see which attributes are highly correlated
```{r}
install.packages("corrplot")
```
```{r}
library(corrplot)
```

```{r}
correlationMatrix <- cor(carrefour)
correlationMatrix
corrplot(correlationMatrix)
```
Let's find attributes which are highly correlated
```{r}
highcorr <- findCorrelation(correlationMatrix, cutoff = 0.75)
highcorr

```
Let's Remove highly correlated features
```{r}
carrefour2 <- carrefour[-highcorr]
```
Let's look at our graphs
install corrplot
```{r}
install.packages("corrplot")
```
load library
```{r}
library(corrplot)
```

```{r}
par(mfrow = c(1,2))
corrplot(correlationMatrix, order = "hclust")
corrplot(cor(carrefour2), order = "hclust")
```

`


